Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
Plot

@@

 \end{tikzpicture}}
 \end{subfigure}
 \hfill
 \begin{subfigure}{.78\textwidth}
   \centering\scriptsize
   \setlength{\figurewidth}{\textwidth}
   \setlength{\figureheight}{.5\figurewidth}
   \pgfplotsset{axis on top}
   \input{./fig/rl.tex}
 \end{subfigure}
 \hfill
 \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
 \label{fig:rl}
\end{figure}

>>>>

An alternative view of the dual variables is that they parameterize approximate likelihoods as was shown in \citep{adam2021dual} we can rewrite the GP posterior in terms of the following approximate normals:
\begin{equation}
 q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\beta}{2}(y_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\tilde{\vy} - \vu)^\top\tilde{\MSigma}^{-1}(\tilde{\vy} - \vu)}  
\end{equation}

@@

 \end{tikzpicture}}
 \end{subfigure}
 \hfill
 \begin{subfigure}{.78\textwidth}
   \centering\scriptsize
   \setlength{\figurewidth}{\textwidth}
   \setlength{\figureheight}{.5\figurewidth}
   \pgfplotsset{axis on top,ymajorgrids,axis line style={draw=none} }
   \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
   \input{./fig/rl.tex}
 \end{subfigure}
 \hfill
 \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
 \label{fig:rl}
\end{figure}
